%
%Academic CV LaTeX Template
% Author: Dubasi Pavan Kumar
% LinkedIn: https://www.linkedin.com/in/im-pavankumar/
% License: MIT
%
% For errors, suggestions, or improvements, please contact:
% Email: pavankumard.pg19.ma@nitp.ac.in
%



\documentclass[a4paper,11pt]{article}

% Package imports
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{DejaVuSerif}
\usepackage{DejaVuSans}
\usepackage{DejaVuSansMono}
%\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}

% Color definitions
\definecolor{darkblue}{RGB}{0,0,139}

% Page layout
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\setlength{\footskip}{5pt} % Addressing fancyhdr warning

% Hyperlink setup (moved after fancyhdr to address warning)
\usepackage{xurl}
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

% Custom box settings
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={},
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt,outer arc=0pt,
}

% URL style
\urlstyle{tt}
\makeatletter
\let\HREF\href
\renewcommand{\href}[2]{\HREF{#1}{\begingroup\UrlFont #2\endgroup}}
\makeatother
% Text alignment
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\circ$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,itemsep=0.5mm]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

% Commands for icon sizing and positioning
\newcommand{\socialicon}[1]{\raisebox{-0.05em}{\resizebox{!}{1em}{#1}}}
\newcommand{\ieeeicon}[1]{\raisebox{-0.3em}{\resizebox{!}{1.3em}{#1}}}

\begin{document}

% Header
\begin{center}
	{\Huge\textbf{Benjamin T. James}}
\end{center}
\vspace{-6mm}

\begin{center}
	\small{
		\socialicon{\faPhone} (314)-703-5233 | \socialicon{\faEnvelope} \href{mailto:benjames@mit.edu}{benjames@mit.edu} |
		\socialicon{\faUser} \url{https://www.mit.edu/~benjames/}
	}
\end{center}
\vspace{-6mm}

\begin{center}
	\small{
		\socialicon{\faBookReader} \href{https://scholar.google.com/citations?user=t0y3zRkAAAAJ}{Google Scholar} |
		\socialicon{\faGithub} \href{https://github.com/benjamin-james}{benjamin-james} |
		\socialicon{\faTwitter} \href{https://twitter.com/\_\_ben\_james\_\_}{@\_\_ben\_james\_\_}
	}
\end{center}
\vspace{-6mm}
\begin{center}
	\small{Cambridge, MA 02139, USA}
\end{center}

\vspace{-4mm}

%% \section{\textbf{Overview}}
%% \vspace{1mm}
%% \small{
%%   Ph.D student seeking a challenging position to leverage my expertise in computational genomics.
%%   Aiming to contribute to innovative projects at the intersection of AI and practical problem-solving in fields such as [specific areas of interest].
%% }
%% \vspace{-2mm}



%% \section{\textbf{Experience}}
%% \vspace{-0.4mm}
%%   \resumeSubHeadingListStart
%%   \resumeSubheading
%%       {{Company A [\href{https://www.companya.com}{\faIcon{globe}}]}}{City, Country}
%%       {Job Title A}{Month Year - Month Year}
%%       \resumeItemListStart
%%         \item Developed [specific achievement] achieving [specific metric] in [specific area]
%%         \item Implemented [technology/method], enhancing [specific aspect] by [specific percentage]
%%         \item Conducted analysis on [specific data], identifying [key findings]
%%         \item Presented findings at [specific event], receiving [specific recognition]
%%       \resumeItemListEnd 
%%   \resumeSubheading
%%     {Company B [\href{https://www.companyb.com}{\faIcon{globe}}]}{Remote}
%%     {Job Title B}{Month Year - Month Year}
%%     \resumeItemListStart
%%       \item Engineered a [specific system/model], improving [specific metric] by [percentage]
%%       \item Developed [specific tool/method], increasing [specific aspect] by [percentage]
%%       \item Implemented [specific system], reducing [specific metric] by [percentage]
%%       \item Conducted [specific test/analysis] to validate [specific aspect]
%%     \resumeItemListEnd
%%   \resumeSubHeadingListEnd
%% \vspace{-6mm}

\section{\textbf{Education}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
\resumeSubheading
{Massachusetts Institute of Technology}{Cambridge, Massachusetts}
{Ph.D in Electrical Engineering and Computer Science, minor in Econometrics}{September 2019 -- August 2026}
\resumeItemListStart
\item GPA: 4.80/5.00
\item Advisor: Manolis Kellis
\resumeItemListEnd

\resumeSubheading
{Massachusetts Institute of Technology}{Cambridge, Massachusetts}
{SM in Electrical Engineering and Computer Science}{September 2019 -- May 2023}
\resumeItemListStart
\item GPA: 4.80/5.00
\item Advisor: Manolis Kellis
\resumeItemListEnd

\resumeSubheading
{University of Tulsa}{Tulsa, Oklahoma}
{BSc in Mathematics, BSc in Computer Science}{Aug 2015 -- May 2019}
\resumeItemListStart
\item GPA: 3.747/4.000
\item Advisor: Hani Z. Girgis
\resumeItemListEnd

%% \resumeSubheading
%% {}{City, Country}
%% {Pre-University Education}{Month Year}
%% \resumeItemListStart
%% \item Grade: XX.X\%
%% \resumeItemListEnd

%% \resumeSubheading
%% {High School Name}{City, Country}
%% {Secondary Education}{Month Year}
%% \resumeItemListStart
%% \item GPA: X.X/10
%% \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-6mm}

\section{\textbf{Projects}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeProject
{Single-cell dissection of the human brain}
{Tools: R, Python, Bash}
{2021 - 2026}
{{}[\href{https://github.com/kellislab/}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
\item Expert level analysis of several large-sample snRNA-seq and snATAC-seq atlases and application towards human disease (Alzheimer's disease, addiction), including several Cell publications (two co-first authorship \textbf{[S.1]},\textbf{[J.11]})
\item Revealed differentially expressed genes and differentially accessibile regions, prioritized genetic variants, and proposed downstream pathways dysregulated in disease
\item Developed peak-gene linking, snATAC-seq/snRNA-seq integration methodology, and gene/enhancer module discovery in service of understanding gene regulatory changes in human disease \textbf{[J.11]}
\item Led computational analysis for a single-cell dissection of the human striatum \textbf{[S.1]}, transcriptomic rescue of mouse chemobrain symptoms \textbf{[J.6]}, and organoid technology \textbf{[J.5]} but played integral role in others
\item Wrote several bespoke scripts across several single-cell projects and organized into \href{https://github.com/kellislab/benj}{this repo} that much of the lab uses to perform analysis at the scale of hundreds of samples
\resumeItemListEnd

\resumeProject
{Single cell genomics module discovery for grouping functional units}
{Tools: Python, R, C++}
{2023-2026}
{{}[\href{https://github.com/kellislab/scdemon}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
\item Developed gene co-expression framework (similar to WGCNA) to categorize differential gene expression across multiple brain regions in Alzheimer's disease \textbf{[J.7]},\textbf{[J.11]}
\item Utilizes PCA loadings from high dimensional genomic assays to relate gene embeddings to functional graphs while accounting for techinical artifacts like sequencing depth
\item Although mature, I am trying to still improve estimation (Q-Q plots, modelling technical artifacts in-model instead of after-model, etc) using high-dimensional statistics and linear algebra
\item Co-developed with Carles Boix, used prominently in \textbf{[J.7]} and \textbf{[J.11]} to interpret differentially expressed genes across multiple cell types and brain regions
\resumeItemListEnd

\resumeProject
{Scalable, spatially-informed clustering for spatial transcriptomics}
{Tools: Python, ARPACK (scipy)}
{2025-2026}
{{}[\href{https://github.com/kellislab/banksy-hd}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
\item Adaptation of the \href{https://doi.org/10.1038/s41588-024-01664-3}{BANKSY algorithm} for high dimensional transcriptomics
\item Newer spatial transcriptomics assays like 10x Genomics Visium HD contain millions of spots per experiment that are not amenable to these methods
\item Tech specific adaptations include a Sinkhorn-Knopp based noise removal (de-striping) and a Laplacian of Gaussian filter (for blob detection) replacing a Gabor filter
\item Sparse incremental Lanczos-based PCA that allows for input matrices to stay sparse, as opposed to the sklearn based IncrementalPCA
\item Designed and implemented alone, with no collaborators and no advisor input
\resumeItemListEnd

\resumeProject
{Linking regulatory elements to their target genes}
{Tools: Python, R, XGBoost}
{2019-2023}
{{}[\href{https://github.com/kellislab/epimap}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
\item Developed a method that links annotated enhancers to target genes by using correlated activity between epigenomes (imputed ChIP-seq) over putative enhancers and corresponding gene expression \textbf{[J.12]},\textbf{[J.9]},\textbf{[P.18]},\textbf{[J.2]}
\item Started as rotation project in Manolis Kellis lab, directly supervised under Carles Boix (1st author of Nature paper), where my contributions placed me as a second author on a Nature paper \textbf{[J.12]}
\item Worked with the ENCODE Distal Regulation group and GENCODE with this method to annotate regulatory elements \textbf{[J.8]},\textbf{[J.4]},\textbf{[P.19]}
\item Later this methodology for linking putative enhancers to genes was extended for single-nucleus ATAC-seq studies for Alzheimer's disease \textbf{[J.11]},\textbf{[J.10]}
\resumeItemListEnd

\resumeProject
{Intelligent clustering of DNA sequences}
{Tools: C++/OpenMP; gdb/valgrind}
{2016-2019}
{{}[\href{https://github.com/BioinformaticsToolsmith/MeShClust}{\textcolor{darkblue}{\faGithub}}]}
\resumeItemListStart
\item Developed a fast method as an undergraduate student to approximate an expensive method for DNA similarity (alignment). \textbf{[J.17]},\textbf{[J.16]},\textbf{[J.14]},\textbf{[J.13]},\textbf{[P.20]}
\item Implemented a fast, concurrent version of the Mean Shift algorithm that scales well for large DNA sets in a manner similar to (H)DBSCAN
\item Self-supervised linear model generates mutations at a known rate and then assigns their similarlity
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{\textbf{Publications} \hfill \textcolor{darkblue}{\scriptsize C=Conference, J=Journal, P=Preprint, S=In Submission, T=Thesis, *=Co-first authorship}}
\vspace{0.2mm}
\small{
	\begin{enumerate}[leftmargin=*, labelsep=0.5em, align=left, widest={[\textbf{S.1}]}, itemindent=0em, label={\textbf{[\arabic*]}]}]

		\item[\textbf{[S.1]}] {Linville*, R. M., \textbf{James*, B. T.}, Galani, K., Ho, L., Shin, J., Oliver, E., Bock, R., Murray, E. M., Louca, M., Oke, O., Wang, C., Engelberg-Cook, E., DeTure, M., Farrell, V., Fitzwalter, B., Pineda, S., Sathitloetsakun, S., Liang, X., Madras, B., and Dickson, D. W., Mash, D. C., Turecki, G., Wheeler, V. C., Alvarez, V. A., Gabuzda, D., Kellis, M., Heiman, M. (2025). Cross-species single cell atlas of the striatum defines cell type and subregion disease vulnerabilities. \textit{Cell}. \textbf{Accepted for publication pending minor revisions}}

		\item[\textbf{[J.2]}] {Boix, C. A., \textbf{James, B. T.}, Park, Y. P., Meuleman, W., \& Kellis, M. (2025). Author Correction: Regulatory genomic circuitry of human disease loci by integrative epigenomics. \textit{Nature}, \textit{643}(8071), E11. \url{https://doi.org/10.1038/s41586-025-09134-4}}

		\item[\textbf{[J.3]}]{Liu, Z., Zhang, S., \textbf{James, B. T.}, Galani, K., Mangan, R. J., Fass, S. B., Liang, C., Wagle, M. M., Boix, C. A., Tanigawa, Y., Yun, S., Sung, Y., Xiong, X., Sun, N., Hou, L., Wohlwend, M., Qiu, M., Han, X., Xiong, L., … Kellis, M. (2025). Single-cell multiregion epigenomic rewiring in Alzheimer’s disease progression and cognitive resilience. \textit{Cell}, \textit{188}(18), 4980–5002.e29. \url{https://doi.org/10.1016/j.cell.2025.06.031}}

		\item[\textbf{[J.4]}]{Mudge, J. M., Carbonell-Sala, S., Diekhans, M., Martinez, J. G., Hunt, T., Jungreis, I., Loveland, J. E., Arnan, C., Barnes, I., Bennett, R., Berry, A., Bignell, A., Cerdán-Vélez, D., Cochran, K., Cortés, L. T., Davidson, C., Donaldson, S., Dursun, C., Fatima, R., … Frankish, A. (2025). GENCODE 2025: reference gene annotation for human and mouse. \textit{Nucleic Acids Research}, \textit{53}(D1), D966–D975. \url{https://doi.org/10.1093/nar/gkae1078}}

		\item[\textbf{[J.5]}]{Stanton, A. E., Bubnys, A., Agbas, E., \textbf{James, B.}, Park, D. S., Jiang, A., Pinals, R. L., Liu, L., Truong, N., Loon, A., Staab, C., Cerit, O., Wen, H.-L., Mankus, D., Bisher, M. E., Lytton-Jean, A. K. R., Kellis, M., Blanchard, J. W., Langer, R., \& Tsai, L.-H. (2025). Engineered 3D immuno-glial-neurovascular human miBrain model. \textit{Proceedings of the National Academy of Sciences}, \textit{122}(42), e2511596122. \url{https://doi.org/10.1073/pnas.2511596122}}

		\item[\textbf{[J.6]}]{Kim, T., \textbf{James, B. T.}, Kahn, M. C., Blanco-Duque, C., Abdurrob, F., Islam, M. R., Lavoie, N. S., Kellis, M., \& Tsai, L.-H. (2024). Gamma entrainment using audiovisual stimuli alleviates chemobrain pathology and cognitive impairment induced by chemotherapy in mice. \textit{Science Translational Medicine}, \textit{16}(737), eadf4601. \url{https://doi.org/10.1126/scitranslmed.adf4601}}

		\item[\textbf{[J.7]}]{Mathys, H., Boix, C. A., Akay, L. A., Xia, Z., Davila-Velderrain, J., Ng, A. P., Jiang, X., Abdelhady, G., Galani, K., Mantero, J., Band, N., \textbf{James, B. T.}, Babu, S., Galiana-Melendez, F., Louderback, K., Prokopenko, D., Tanzi, R. E., Bennett, D. A., Tsai, L.-H., \& Kellis, M. (2024). Single-cell multiregion dissection of Alzheimer’s disease. \textit{Nature}, \textit{632}(8026), 858–868. \url{https://doi.org/10.1038/s41586-024-07606-7}}

		\item[\textbf{[J.8]}]{Frankish, A., Carbonell-Sala, S., Diekhans, M., Jungreis, I., Loveland, J. E., Mudge, J. M., Sisu, C., Wright, J. C., Arnan, C., Barnes, I., Banerjee, A., Bennett, R., Berry, A., Bignell, A., Boix, C., Calvet, F., Cerdán-Vélez, D., Cunningham, F., Davidson, C., … Flicek, P. (2023). GENCODE: reference annotation for the human and mouse genomes in 2023. \textit{Nucleic Acids Research}, \textit{51}(D1), D942–D949. \url{https://doi.org/10.1093/nar/gkac1071}}

		\item[\textbf{[J.9]}]{Hou, L., Xiong, X., Park, Y., Boix, C., \textbf{James, B.}, Sun, N., He, L., Patel, A., Zhang, Z., Molinie, B., Van Wittenberghe, N., Steelman, S., Nusbaum, C., Aguet, F., Ardlie, K. G., \& Kellis, M. (2023). Multitissue H3K27ac profiling of GTEx samples links epigenomic variation to disease. \textit{Nature Genetics}, \textit{55}(10), 1665–1676. \url{https://doi.org/10.1038/s41588-023-01509-5}}

		\item[\textbf{[J.10]}]{Sun, N., Victor, M. B., Park, Y. P., Xiong, X., Scannail, A. N., Leary, N., Prosper, S., Viswanathan, S., Luna, X., Boix, C. A., \textbf{James, B. T.}, Tanigawa, Y., Galani, K., Mathys, H., Jiang, X., Ng, A. P., Bennett, D. A., Tsai, L.-H., \& Kellis, M. (2023). Human microglial state dynamics in Alzheimer’s disease progression. \textit{Cell}, \textit{186}(20), 4386–4403.e29. \url{https://doi.org/10.1016/j.cell.2023.08.037}}

		\item[\textbf{[J.11]}]{Xiong*, X., \textbf{James*, B. T.}, Boix*, C. A., Park, Y. P., Galani, K., Victor, M. B., Sun, N., Hou, L., Ho, L.-L., Mantero, J., Scannail, A. N., Dileep, V., Dong, W., Mathys, H., Bennett, D. A., Tsai, L.-H., \& Kellis, M. (2023). Epigenomic dissection of Alzheimer’s disease pinpoints causal variants and reveals epigenome erosion. \textit{Cell}, \textit{186}(20), 4422–4437.e21. \url{https://doi.org/10.1016/j.cell.2023.08.040}}

		\item[\textbf{[J.12]}]{Boix, C. A., \textbf{James, B. T.}, Park, Y. P., Meuleman, W., \& Kellis, M. (2021). Regulatory genomic circuitry of human disease loci by integrative epigenomics. \textit{Nature}, \textit{590}(7845), 300–307. \url{https://doi.org/10.1038/s41586-020-03145-z}}

		\item[\textbf{[J.13]}]{Girgis, H. Z., \textbf{James, B. T.}, \& Luczak, B. B. (2021). Identity: rapid alignment-free prediction of sequence alignment identity scores using self-supervised general linear models. \textit{Nar Genomics and Bioinformatics}, \textit{3}(1), lqab001. \url{https://doi.org/10.1093/nargab/lqab001}}

		\item[\textbf{[J.14]}]{Velasco, A. II, \textbf{James, B. T.}, Wells, V. D., \& Girgis, H. Z. (2020). Look4TRs: a de novo tool for detecting simple tandem repeats using self-supervised hidden Markov models. \textit{Bioinformatics}, \textit{36}(2), 380–387. \url{https://doi.org/10.1093/bioinformatics/btz551}}

		\item[\textbf{[J.15]}]{Luczak, B. B., \textbf{James, B. T.}, \& Girgis, H. Z. (2019). A survey and evaluations of histogram-based statistics in alignment-free sequence comparison. \textit{Briefings in Bioinformatics}, \textit{20}(4), 1222–1237. \url{https://doi.org/10.1093/bib/bbx161}}

		\item[\textbf{[J.16]}]{Zielezinski, A., Girgis, H. Z., Bernard, G., Leimeister, C.-A., Tang, K., Dencker, T., Lau, A. K., Röhling, S., Choi, J. J., Waterman, M. S., Comin, M., Kim, S.-H., Vinga, S., Almeida, J. S., Chan, C. X., \textbf{James, B. T.}, Sun, F., Morgenstern, B., \& Karlowski, W. M. (2019). Benchmarking of alignment-free sequence comparison methods. \textit{Genome Biology}, \textit{20}(1), 144. \url{https://doi.org/10.1186/s13059-019-1755-7}}

		\item[\textbf{[J.17]}]{\textbf{James, B. T.}, Luczak, B. B., \& Girgis, H. Z. (2018). MeShClust: an intelligent tool for clustering DNA sequences. \textit{Nucleic Acids Research}, \textit{46}(14), e83. \url{https://doi.org/10.1093/nar/gky315}}

		\item[\textbf{[P.18]}]{Middelbeek, R. J. W., Yang, J., Nigro, P., \textbf{James, B.}, Papadopoulos, D., Simpson, L. K., Park, J., Vamvini, M., Ho, L.-L., Zhang, H., Carbone, N. P., Hirshman, M. F., Kellis, M., \& Goodyear, L. J. (2025). \textit{Type 2 Diabetes and Obesity Alter Exercise Training-Induced Transcriptional Adaptations to Subcutaneous White Adipose Tissue}. bioRxiv. \url{https://doi.org/10.1101/2025.10.11.681273}}

		\item[\textbf{[P.19]}]{Gschwind, A. R., Mualim, K. S., Karbalayghareh, A., Sheth, M. U., Dey, K. K., Jagoda, E., Nurtdinov, R. N., Xi, W., Tan, A. S., Jones, H., Ma, X. R., Yao, D., Nasser, J., Avsec, Ž., \textbf{James, B. T.}, Shamim, M. S., Durand, N. C., Rao, S. S. P., Mahajan, R., … Engreitz, J. M. (2023). \textit{An encyclopedia of enhancer-gene regulatory interactions in the human genome}. bioRxiv. \url{https://doi.org/10.1101/2023.11.09.563812} \textbf{Soon to be in Nature, pending rest of package approval}}

		\item[\textbf{[P.20]}]{\textbf{James, B. T.}, \& Girgis, H. Z. (2018). \textit{MeShClust2: Application of alignment-free identity scores in clustering long DNA sequences}. bioRxiv. \url{https://doi.org/10.1101/451278}}

		\item[\textbf{[T.21]}]{\textbf{James, B. T.} (2023). \textit{Correlation-based Linking of Epigenomic Regions to Target Genes in Bulk and Single Cell Epigenomic Data} [Thesis, Massachusetts Institute of Technology]. \url{https://dspace.mit.edu/handle/1721.1/151538}}
		      %% \item[\textbf{[C.1]}] Your Name, et al. (Year). \href{https://doi.org/XX.XXXX/XXXXXXX.XXXX.XXXXXXX}{\textbf{Title of Conference Paper}}. In \textit{Name of Conference Proceedings}, pp. XX-XX. Publisher. Date, Location. DOI: XX.XXXX/XXXXXXX.XXXX.XXXXXXX

		      %% \item[\textbf{[S.1]}] Your Name, et al. (Year). \textbf{Title of Submitted Paper}. Manuscript submitted for publication in \textit{Journal Name}.

		      %% \item[\textbf{[P.1]}] Inventor 1, Your Name, Inventor 3, et al. (Year). \href{https://patentoffice.gov/patent/XXXXXXXXX}{\textbf{Title of Patent}}. Patent Office, Patent No. XXXXXXXXX. Registration Date: Date, Grant Date: Date, Publication Date: Date.

		      %% \item[\textbf{[J.1]}] Author 1, Your Name, Author 3, et al. (Year). \href{https://doi.org/XX.XXXX/XXXXX.XXXX.XXXXXXX}{\textbf{Title of Journal Article}}. \textit{Journal Name}, Vol. XX, Issue X, pp. XXX-XXX. DOI: XX.XXXX/XXXXX.XXXX.XXXXXXX
	\end{enumerate}
}


\section{\textbf{Skills}}
\vspace{-0.4mm}
\resumeHeadingSkillStart
\resumeSubItem{Programming Languages:}
{R and Python (Daily use), C++ (+pybind11/Rcpp), Golang, Bash/POSIX sh, C, AWK \& Perl, Julia, Common Lisp}
\resumeSubItem{Research-specific Packages and Tools:}
{Bioconductor, scverse, samtools/bedtools, Eigen, NumPy/SciPy/SK-Learn, Snakemake \& Nextflow, brms}
\resumeSubItem{DevOps/MLOps:}
{De-facto manager of two lab-wide compute clusters, managing software (Lmod, conda, Docker, singularity environments, CUDA/NV admin, Terraform, Ansible, etc). Experienced Linux user (Debian/Gentoo user since 2014), see \href{https://github.com/benjamin-james/dotfiles}{my dotfiles}, formerly an ArchLinux \href{https://aur.archlinux.org/packages?SeB=m&K=benjamin-james}{maintainer}}
\resumeSubItem{Side projects:}
{Wrote an \textbf{agentic} harness tool to specify disposable agent virtual machines \href{https://github.com/benjamin-james/agentctl}{\faGithub} and deploy them \href{https://github.com/benjamin-james/dotfiles/blob/master/bin/vm}{\faGithub},
	Contributed the dot-product distance into the \href{https://github.com/eddelbuettel/rcppannoy}{RcppAnnoy} package required by R genomics libraries \href{https://github.com/eddelbuettel/rcppannoy/pull/78}{\faGithub},
	Wrote the sparse-matrix math for the \href{https://github.com/pinellolab/pychromVAR}{pychromVAR} package for transcription factor enrichment in snATAC-seq \href{https://github.com/pinellolab/pychromVAR/pull/13}{\faGithub},
	wrote a complete BF compiler \href{https://github.com/benjamin-james/brainfuck}{\faGithub} and a Pascal compiler frontend \href{https://github.com/benjamin-james/pascal-compiler}{\faGithub} both in C, wrote and deployed a multi-user webapp on a VPS \href{https://github.com/benjamin-james/cfb_survivor_pool}{\faGithub} (Apache/Flask/PostgresQL)}
\resumeHeadingSkillEnd

\section{\textbf{Honors and Awards}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeProject
{NSF GRFP}
{National Science Foundation}
{May 2019}
{{}}%[\href{https://award-link-a.com}{\textcolor{darkblue}{\faIcon{globe}}}]}
\resumeItemListStart
\item Awarded NSF GRFP during undergraduate tenure
\resumeItemListEnd

\resumeProject
{Cronin Fellowship}
{MIT EECS department}
{April 2019}
{{}}
\resumeItemListStart
\item MIT departmental (EECS) fellowship for exceptional Ph.D applicants
\resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-6mm}
%% \section{\textbf{Leadership Experience}}
%% \vspace{-0.4mm}
%% \resumeSubHeadingListStart
%% \resumeProject
%%   {Leadership Role A}
%%   {Organization/Institution Name}
%%   {Month Year - Month Year}
%%   {{}[\href{https://organization-a-link.com}{\textcolor{darkblue}{\faIcon{globe}}}]}
%% \resumeItemListStart
%%   \item Key responsibility or achievement in this role
%%   \item Quantifiable impact or improvement made during tenure
%%   \item Initiative taken or project led
%% \resumeItemListEnd

%% \resumeProject
%%   {Leadership Role B}
%%   {Organization/Institution Name}
%%   {Month Year - Month Year}
%%   {{}[\href{https://organization-b-link.com}{\textcolor{darkblue}{\faIcon{globe}}}]}
%% \resumeItemListStart
%%   \item Key responsibility or achievement in this role
%%   \item Quantifiable impact or improvement made during tenure
%%   \item Initiative taken or project led
%% \resumeItemListEnd

%% \resumeSubHeadingListEnd

%% \vspace{-6mm}

%% \section{\textbf{Volunteer Experience}}
%% \vspace{-0.4mm}
%% \resumeSubHeadingListStart
%% \resumeProject
%%   {Volunteer Role A}
%%   {Organization Name}
%%   {Month Year - Month Year}
%%   {{}[\href{https://volunteer-org-a-link.com}{\textcolor{darkblue}{\faIcon{globe}}}]}
%% \resumeItemListStart
%%   \item Key responsibility or contribution in this role
%%   \item Impact of your volunteer work
%%   \item Skills developed or applied during this experience
%% \resumeItemListEnd

%% \resumeProject
%%   {Volunteer Role B}
%%   {Organization Name}
%%   {Month Year - Present}
%%   {{}[\href{https://volunteer-org-b-link.com}{\textcolor{darkblue}{\faIcon{globe}}}]}
%% \resumeItemListStart
%%   \item Key responsibility or contribution in this role
%%   \item Impact of your volunteer work
%%   \item Skills developed or applied during this experience
%% \resumeItemListEnd

%% \resumeSubHeadingListEnd
%% \vspace{-6mm}

%% \section{\textbf{Professional Memberships}}
%% \vspace{-0.4mm}
%% \resumeSubHeadingListStart
%% \resumePOR{Professional Organization A}
%%     {, Membership ID: XXXXXXXX}
%%     {Month Year - Present}
%% \resumePOR{Professional Organization B}
%%     {, \href{https://membership-certificate-link.com}{Membership ID: XXXXXXXX}}
%%     {Month Year - Present}
%% \resumePOR{Professional Organization C}
%%     {, \href{https://membership-certificate-link.com}{Membership ID: XXXXXXXX}}
%%     {Month Year - Present}

%% \resumeSubHeadingListEnd
%% \vspace{-6mm}

%% \section{\textbf{Certifications}}
%% \vspace{-0.2mm}
%% \resumeSubHeadingListStart
%% \resumePOR{}{\href{https://certification-link-a.com}{
%% \textbf{Certification A}
%% }}{Month Year}
%% \resumePOR{}{
%% \textbf{Certifying Body:} {{\href{https://certification-link-b.com}{Certification B}}}}{Month Year}
%% \resumePOR{}{
%% \textbf{Certifying Body:} {{\href{https://certification-link-c.com}{Certification C}}}}{Month Year}
%% \resumePOR{}{\href{https://certification-link-d.com}{
%% \textbf{Certification D}
%% }}{Month Year}

%% \resumeSubHeadingListEnd
%% \vspace{-6mm}

%% \section{\textbf{Additional Information}}
%% \vspace{-0.4mm}
%% \small{
%% \textbf{Languages:} Language A (Proficiency level), Language B (Proficiency level), Language C (Proficiency level)

%% \textbf{Interests:} Interest 1, Interest 2, Interest 3, Interest 4
%% }
%% \vspace{-4mm}


%% \section{\textbf{References}}
%% \vspace{-0.2mm}
%% \small{
%% \begin{enumerate}[leftmargin=*,labelsep=2mm]
%% \item \textbf{Reference Person 1}\\
%%    Job Title, Department\\
%%    Organization/Institution Name\\
%%    Email: email1@example.com\\
%%    Phone: +X-XXX-XXX-XXXX\\
%%    \textit{Relationship: [e.g., Thesis Advisor, Manager, etc.]}

%% \item \textbf{Reference Person 2}\\
%%    Job Title, Department\\
%%    Organization/Institution Name\\
%%    Email: email2@example.com\\
%%    Phone: +X-XXX-XXX-XXXX\\
%%    \textit{Relationship: [e.g., Project Supervisor, Colleague, etc.]}

%% \item \textbf{Reference Person 3}\\
%%    Job Title, Department\\
%%    Organization/Institution Name\\
%%    Email: email3@example.com\\
%%    Phone: +X-XXX-XXX-XXXX\\
%%    \textit{Relationship: [e.g., Mentor, Collaborator, etc.]}
%% \end{enumerate}
%% }

\end{document}
